Expert-In-The-Loop Causal Discovery: \\ Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Improves testing section

\subsection{Testing DAG Using CI Tests}
Our structure learning algorithm uses the idea of testing DAGs using CI tests.
In this section, we give an example of how this model testing works in
practice. We take the example of the MEC learned by the PC algorithm in
Figure~\ref{fig:intro}(b) using $ N=800 $. We first orient all the undirected
edges in the model based on our domain knowledge to obtain a DAG. In this case
we only have one undirected edge between \emph{Marital Status} and
\emph{Relationship} that we orient as \emph{Marital Status} $ \rightarrow $
\emph{Relationship} . We can then test the implied CIs of the DAG using our
dataset. Figure~\ref{fig:ci_table} shows the result of this testing on some of
the implied CIs. If we use a p-value threshold of $ 0.05 $, the first $ 2 $
implied CIs hold in the data whereas the remaining tests fail. One of the ways
to fix these failing tests is to add an edge between the variable pair $ X $
and $ Y $. While this method helps us in finding variable pairs where we need
to add an edge, it does not give us any information about the orientation of
this edge. We would have to rely on domain knowledge to determine this
orientation.

>>>>

\subsection{Testing DAG Using CI Tests}
Our structure learning algorithm uses the idea of testing DAGs using CI tests.
In this section, we show an example of how this model testing works in
practice. We take the example of the MEC learned by the PC algorithm in
Figure~\ref{fig:intro}(b) using $ N=800 $. We first orient all the undirected
edges in the model based on our domain knowledge to obtain a DAG. In this case
we only have one undirected edge between \emph{Marital Status} and
\emph{Relationship} that we orient as \emph{Marital Status} $ \rightarrow $
\emph{Relationship}. We can then test each of the implied CIs of the DAG
against our dataset using a statistical test. Figure~\ref{fig:ci_table} shows
some of the implied CIs of the model and the corresponding p-value of
statistical test. Using a p-value threshold of $ 0.05 $, we can determine that
the first $2$ implied CIs hold in the data while the remaining two do not.
These failing tests tell us that there is residual association between these
variable pairs that is currently not being explained by the DAG. This method,
however, does not give us any information on the reason, such as there is a
direct or indirect effect, or a confounding variable, behind this observed
association. To fix these failing tests, we still have to rely on domain
knowledge to determine the type of relationship and the causal directions
between these variables.
